Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
Introduction.

\section{Non-kissing complex}

@@

\section{Accordion complex, slalom complex, and non-crossing complex}

@@

\begin{corollary}
The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.
\end{corollary}

>>>>

\section{Introduction}

BLAH BLAH BLAH

The two main objects of our study will be locally gentle algebras and dissections of surfaces.
Our first main result is that these two classes of objects are essentially the same.

\begin{theorem*}[\ref{thm:bijectionLocallyGentleAndSurfaces}]
 There is an explicit bijection between the set of isomorphism classes of locally gentle bound quivers and the set of homeomorphism classes of oriented marked surfaces with boundary and a pair of dual cellular dissections.
\end{theorem*}

On the algebraic side, we extend the study of walks from the gentle to the locally gentle case, and define a notion of compatibility called non-kissing (see Section \ref{sec:nonKissingComplex}).
On the geometric side, we extend the study of dissections, accordions and slaloms from the case of the disk to the case of an arbitrary surface, and define a notion of compatibility called non-crossing (see Section \ref{sec:accordionSlalomNonCrossingComplexes}).
The combinatorial information contained in these notions is encoded in simplicial complexes: the non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC$.

\begin{theorem*}[\ref{thm:complexesCoincide}]
 The complexes~$\NKC$ and~$\NCC$ are isomorphic.
\end{theorem*}

Finally, we show that these complexes have very nice combinatorial properties.

\begin{theorem*}[\ref{prop:purity} and \ref{coro:thin}]
 The complexes~$\NKC$ and~$\NCC$ are pure and thin.  Their dimension is computed, and mutation is explicitly described.
\end{theorem*}

Consequences on the representation theory of locally gentle algebras will be investigated in a future project.

\section{Non-kissing complex}\label{sec:nonKissingComplex}

@@

\section{Accordion complex, slalom complex, and non-crossing complex}\label{sec:accordionSlalomNonCrossingComplexes}

@@

\begin{corollary}
\label{coro:thin}
The non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$.  Moreover, it is thin and is a pseudomanifold without boundary.
\end{corollary}
